---
title: "R Notebook"
output: html_notebook
---
Lets analyse Brainhack ego network

```{r}
library(tidyverse)
library(rtweet)
(my_followers <- get_followers("BrainhackW"))
(my_friends <- get_friends("BrainhackW"))
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
my_friends %>% 
  select(user_id) %>% 
  mutate(i_follow = TRUE) %>% 
  full_join(my_followers %>% mutate(follows_me = TRUE), by = 'user_id') %>% 
  mutate_all(funs(replace(., which(is.na(.)), FALSE))) %>% 
  select(2:3) %>% table
```

```{r}
all_users <- bind_rows(my_friends, my_followers) %>% 
 distinct(user_id)
length(all_users)
```
```{r}
user_details <- lookup_users(all_users$user_id)
```

